Pool Model

### 2023-12-20 pool_model.tex
adapt spatial figures
- add titles
- group two of them together
Corrections to plot names
make title smaller and add authors with affiliations
formatting
rename section; rename species from 1/2 to A/B; write some introductory material

\title{Pool Model Paper}
\author{Polina Gaindrik}

@@

\section{Spatial Limitations}
As described above, the proposed above model operates with the total number of the bacterial counts for different species and states in the system not accounting for their spatial distributions.
Assuming that the bacteria is uniformly distributed we can simplify the problem to the system of the \acp{ode}.
However, in reality spatial effects play significant role for population survival forcing some species develop such competitive mechanism as cell adhesion to surfaces in the areas rich with nutritients~\cite{htuson_bacteriasurface_2013}.

@@

Therefore, it is rather important to establish the limitations for the model application.\\

@@

    \includegraphics[width=0.5\textwidth]{Figures/snapshot_00000000.png}%
    \includegraphics[width=0.5\textwidth]{Figures/snapshot_00006500.png}\\
    \includegraphics[width=0.5\textwidth]{Figures/snapshot_00013000.png}%
    \includegraphics[width=0.5\textwidth]{Figures/snapshot_00020000.png}%

@@

    \includegraphics[width=0.6\textwidth]{Figures/cell_growth.pdf}

@@

    \includegraphics[width=0.6\textwidth]{Figures/lag_phase.pdf}

@@

    \label{fig:spatial-lag-phase}
    \includegraphics[width=0.6\textwidth]{Figures/entropy.pdf}
    \label{fig:spatial-entropy}

@@

        \dot{L_1} = -\lambda_1 R L_1\\
        \dot{G_1} = \lambda_1 R L_1 + \alpha_1 R G_1\\
        \dot{L_2} = -\lambda_2 R L_2\\
        \dot{G_2} = \lambda_2 R L_2 + \frac{\alpha_2}{1 + \mu_I I} R G_2\\

@@

        \dot{R} = -\frac{\alpha_1}{N_t} R G_1-\frac{\alpha_2}{(1 + \mu_I I) N_t} R G_2 \\
        \dot{I} = \kappa G_1

>>>>

\title{Pool Model}
\author{
    Polina Gaindrik\textsuperscript{1},
    Jonas Pleyer\textsuperscript{1}
    and Christian Fleck\textsuperscript{1}
}

\date{
    \footnotesize
    \textsuperscript{\textbf{1}}Freiburg Center for Data Analysis and Modeling
}

@@

\section{Spatial Effects}
As described above, the proposed model operates with the total number of the bacterial counts for different species and states in the system not accounting for their spatial distributions.
Assuming that the bacterial system is uniformly distributed (sometimes also called 'well-stirred') we can simplify the problem to a system of \acp{ode}.
However, in reality spatial effects can play a significant role for population survival forcing some species develop competitive mechanisms such as cell adhesion to surfaces in the areas rich with nutritients~\cite{htuson_bacteriasurface_2013}.

@@

These effects can only be treated with a spatial model that is able to describe the observed effects.\\

@@

    \includegraphics[width=0.49\textwidth]{Figures/snapshot_00000000.png}\hspace{0.02\textwidth}%
    \includegraphics[width=0.49\textwidth]{Figures/snapshot_00006500.png}\vspace{0.02\textwidth}\\
    \includegraphics[width=0.49\textwidth]{Figures/snapshot_00013000.png}\hspace{0.02\textwidth}%
    \includegraphics[width=0.49\textwidth]{Figures/snapshot_00020000.png}%

@@

    \includegraphics[width=0.6\textwidth]{Figures/spatial_cell_growth.png}

@@

    \includegraphics[width=0.5\textwidth]{Figures/lag_phase.png}%
    \includegraphics[width=0.5\textwidth]{Figures/entropy.png}
    % TODO difference to pool model

@@

    \label{fig:spatial-lag-phase-entropy}

@@

        \dot{L_A} = -\lambda_A R L_A\\
        \dot{G_A} = \lambda_A R L_A + \alpha_A R G_A\\
        \dot{L_B} = -\lambda_B R L_B\\
        \dot{G_B} = \lambda_B R L_B + \frac{\alpha_B}{1 + \mu_I I} R G_B\\

@@

        \dot{R} = -\frac{\alpha_A}{N_t} R G_A-\frac{\alpha_B}{(1 + \mu_I I) N_t} R G_B \\
        \dot{I} = \kappa G_A
